Ethereum: A Secure Decentralised Generalised Transaction Ledger \\ {\smaller \textbf{Proof-of-Concept V}}

### 2014-05-20 Paper.tex
manifest -> receipt
Min gas limit of 10000.
Use canon order in non-formal text.
Rid ourselves of 32-zero trie roots.

\begin{description}
\item[parentHash] The SHA3 256-bit hash of the parent block, in its entirety; formally $H_p$.
\item[unclesHash] The SHA3 256-bit hash of the uncles list portion of this block; formally $H_u$.
\item[coinbase] The 160-bit address to which all fees collected from the successful mining of this block be transferred; formally $H_b$.
\item[stateRoot] The SHA3 256-bit hash of the root node of the state trie, after all transactions are executed and finalisations applied; formally $H_r$.
\item[transactionsTrie] The SHA3 256-bit hash of the root node of the trie structure populated with each transaction in the transactions list portion of the block; formally $H_t$.
\item[difficulty] A scalar value corresponding to the difficulty level of this block. This can be calculated from the previous block's difficulty level and the timestamp; formally $H_d$.
\item[timestamp] A scalar value equal to the reasonable output of Unix's time() at this block's inception; formally $H_s$.
\item[number] A scalar value equal to the number of ancestor blocks. The genesis block has a number of zero; formally $H_i$.
\item[minGasPrice] A scalar value equal to the minimum price of gas a transaction must have provided in order to be sufficient for inclusion by this miner in this block; formally $H_m$.
\item[gasLimit] A scalar value equal to the current limit of gas expenditure per block; formally $H_l$.
\item[gasUsed] A scalar value equal to the total gas used in transactions in this block; formally $H_u$.
\item[extraData] An arbitrary byte array containing data relevant to this block. With the exception of the genesis block, this must be 32 bytes or fewer; formally $H_x$.
\item[nonce] A 256-bit hash which proves that a sufficient amount of computation has been carried out on this block; formally $H_n$.
\end{description}

@@

\subsubsection{Transaction Manifest}

@@

The canonical gas limit of a block of header $H$ is defined as $L(H)$:
\begin{eqnarray}
L(H) & \equiv & \begin{cases}
10^6 & \text{if} \quad H_i = 0\\
L'(H) & \text{otherwise}
\end{cases}\\
L'(H) & \equiv & \big\lfloor \frac{1023 {P(H)_H}_l + \lfloor \frac{6}{5}{P(H)_H}_u \rfloor}{1024}\big\rfloor
\end{eqnarray}

@@

\section{Modified Merkle Patricia Tree}\label{app:trie}
The modified Merkle Patricia tree (trie) provides a persistent data structure to map between arbitrary-length binary data (byte arrays). It is defined in terms of a mutable data structure to map between 256-bit binary fragments and arbitrary-length binary data, typically implemented as a database. The core of the trie, and its sole requirement in terms of the protocol specification is to provide a single 32-byte value that identifies a given set of key-value pairs. It is left as an implementation consideration to store and maintain the structure of the trie in a manner the allows effective and efficient realisation of the protocol.

@@

We define the function $\texttt{\small TRIE}$, which evaluates to the root of the trie that represents this set when encoded in this structure. The empty trie is defined as being a 256-bit hash of zeroes, $0_{256}$:`
\begin{equation}
\texttt{\small TRIE}(\mathfrak{I}) \equiv \begin{cases}
0_{256} & \text{if} \quad \mathfrak{I} = \varnothing \\
n(y(\mathfrak{I}), 0) & \text{otherwise}
\end{cases}
\end{equation}

We assume a function $n$, the trie's node cap function. When composing a node, we use RLP to encode the structure. As a means of reducing storage complexity, for nodes whose composed RLP is fewer than 32 bytes, we store the RLP directly; for those larger we assert prescience of the byte array whose SHA3 hash evaluates to our reference. Thus we define in terms of $c$, the node composition function:
\begin{equation}
n(\mathfrak{I}, i) \equiv \begin{cases}
() & \text{if} \quad \mathfrak{I} = \varnothing \\
c(\mathfrak{I}, i) & \text{if} \quad \lVert c(\mathfrak{I}, i)\rVert < 32 \\
\texttt{\small SHA3}(c(\mathfrak{I}, i)) & \text{otherwise}
\end{cases}
\end{equation}

@@

The genesis block is 13 items, and is specified thus:
\begin{equation}
\big( \big( 0_{256}, \mathtt{\tiny SHA3}\big(\mathtt{\tiny RLP}\big( () \big)\big), 0_{160}, stateRoot, 0_{256}, 2^{22}, 0, 0, 1000000, 0, 0, (), \mathtt{\tiny SHA3}\big( (42) \big) \big), (), () \big)
\end{equation}

Where $0_{256}$ refers to the parent and state and transaction root hashes, a 256-bit hash which is all zeroes; $0_{160}$ refers to the coinbase address, a 160-bit hash which is all zeroes; $2^{22}$ refers to the difficulty; 0 refers to the timestamp (the Unix epoch); $()$ refers to the extradata and the sequences of both uncles and transactions, all empty. $\mathtt{\tiny SHA3}\big( (42) \big)$ refers to the SHA3 hash of a byte array of length one whose first and only byte is of value 42. $\mathtt{\tiny SHA3}\big(\mathtt{\tiny RLP}\big( () \big)\big)$ value refers to the hash of the uncle lists in RLP, both empty lists.

>>>>

\begin{description}
\item[parentHash] The SHA3 256-bit hash of the parent block, in its entirety; formally $H_p$.
\item[unclesHash] The SHA3 256-bit hash of the uncles list portion of this block; formally $H_u$.
\item[coinbase] The 160-bit address to which all fees collected from the successful mining of this block be transferred; formally $H_b$.
\item[stateRoot] The SHA3 256-bit hash of the root node of the state trie, after all transactions are executed and finalisations applied; formally $H_r$.
\item[transactionsTrie] The SHA3 256-bit hash of the root node of the trie structure populated with each transaction in the transactions list portion of the block; formally $H_t$.
\item[difficulty] A scalar value corresponding to the difficulty level of this block. This can be calculated from the previous block's difficulty level and the timestamp; formally $H_d$.
\item[number] A scalar value equal to the number of ancestor blocks. The genesis block has a number of zero; formally $H_i$.
\item[minGasPrice] A scalar value equal to the minimum price of gas a transaction must have provided in order to be sufficient for inclusion by this miner in this block; formally $H_m$.
\item[gasLimit] A scalar value equal to the current limit of gas expenditure per block; formally $H_l$.
\item[gasUsed] A scalar value equal to the total gas used in transactions in this block; formally $H_u$.
\item[timestamp] A scalar value equal to the reasonable output of Unix's time() at this block's inception; formally $H_s$.
\item[extraData] An arbitrary byte array containing data relevant to this block. With the exception of the genesis block, this must be 32 bytes or fewer; formally $H_x$.
\item[nonce] A 256-bit hash which proves that a sufficient amount of computation has been carried out on this block; formally $H_n$.
\end{description}

@@

\subsubsection{Transaction Receipt}

@@

The canonical gas limit of a block of header $H$ is defined as $L(H)$:
\begin{eqnarray}
L(H) & \equiv & \begin{cases}
10^6 & \text{if} \quad H_i = 0\\
10^4 & \text{if} \quad L'(H) < 10^4\\
L'(H) & \text{otherwise}
\end{cases}\\
L'(H) & \equiv & \big\lfloor \frac{1023 {P(H)_H}_l + \lfloor \frac{6}{5}{P(H)_H}_u \rfloor}{1024}\big\rfloor
\end{eqnarray}

@@

\section{Modified Merkle Patricia Tree}\label{app:trie}
The modified Merkle Patricia tree (trie) provides a persistent data structure to map between arbitrary-length binary data (byte arrays). It is defined in terms of a mutable data structure to map between 256-bit binary fragments and arbitrary-length binary data, typically implemented as a database. The core of the trie, and its sole requirement in terms of the protocol specification is to provide a single value that identifies a given set of key-value pairs, which may either a 32 byte sequence or the empty byte sequence. It is left as an implementation consideration to store and maintain the structure of the trie in a manner the allows effective and efficient realisation of the protocol.

@@

We define the function $\texttt{\small TRIE}$, which evaluates to the root of the trie that represents this set when encoded in this structure. The empty trie is defined as being a the empty byte sequence, $()$:
\begin{equation}
\texttt{\small TRIE}(\mathfrak{I}) \equiv \begin{cases}
() & \text{if} \quad \mathfrak{I} = \varnothing \\
\texttt{\small SHA3}(c(\mathfrak{I}, 0)) & \text{otherwise}
\end{cases}
\end{equation}

We also assume a function $n$, the trie's node cap function. When composing a node, we use RLP to encode the structure. As a means of reducing storage complexity, for nodes whose composed RLP is fewer than 32 bytes, we store the RLP directly; for those larger we assert prescience of the byte array whose SHA3 hash evaluates to our reference. Thus we define in terms of $c$, the node composition function:
\begin{equation}
n(\mathfrak{I}, i) \equiv \begin{cases}
() & \text{if} \quad \mathfrak{I} = \varnothing \\
c(\mathfrak{I}, i) & \text{if} \quad \lVert c(\mathfrak{I}, i)\rVert < 32 \\
\texttt{\small SHA3}(c(\mathfrak{I}, i)) & \text{otherwise}
\end{cases}
\end{equation}

@@

The genesis block is 13 items, and is specified thus:
\begin{equation}
\big( \big( 0_{256}, \mathtt{\tiny SHA3}\big(\mathtt{\tiny RLP}\big( () \big)\big), 0_{160}, stateRoot, (), 2^{22}, 0, 0, 1000000, 0, 0, (), \mathtt{\tiny SHA3}\big( (42) \big) \big), (), () \big)
\end{equation}

Where $0_{256}$ refers to the parent hash, a 256-bit hash which is all zeroes; $0_{160}$ refers to the coinbase address, a 160-bit hash which is all zeroes; $2^{22}$ refers to the difficulty; 0 refers to the timestamp (the Unix epoch); $()$ refers to the transaction trie root, extradata and the sequences of both uncles and transactions, all empty. $\mathtt{\tiny SHA3}\big( (42) \big)$ refers to the SHA3 hash of a byte array of length one whose first and only byte is of value 42. $\mathtt{\tiny SHA3}\big(\mathtt{\tiny RLP}\big( () \big)\big)$ value refers to the hash of the uncle lists in RLP, both empty lists.
